---
title: "Opening the Black Box on Intl Aid Data Section"
author: "Jack Hasler"
date: "August 3, 2018"
header-includes:
  - \usepackage{rotating, graphicx}
output:
  pdf_document: default
  html_document: default
---

So this is the document for preparing and presenting results. Moving things over from various other files. The goal of this is to be a working document that can eventually become an appendix to the paper. We'll pull our main models from here and keep the others as robustness checks.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

Importing the libraries that we'll need for all of the following projects.

```{r results=FALSE, message=FALSE}
library(readr)
library(tidyverse)
library(countrycode)
library(car)
library(plm)
library(readxl)
library(wbstats)
library(stargazer)
library(kableExtra)
library(knitr)
```

Gonna break this into three big sections for now. (1) Analysis by Recipient (target?) country, (2) Analysis by donor-recipient dyad, and (3) Subnational analysis. If there are not some descriptive statistics in every section, there should be!

##Analysis by Recipient-Year


```{r import_codes, message = FALSE}
#Importing channel codes
modified_crs_channel_codes <- read_delim("new_channel_codes.csv",",", escape_double = FALSE, trim_ws = TRUE)

#selecting and renaming as necessary
channel_codes <- modified_crs_channel_codes %>%
  select(`Channel ID`, ch_type,ch_identity) %>%
  rename(code = `Channel ID`)
rm(modified_crs_channel_codes)
#turning into factors
channel_codes$ch_type <- as.factor(channel_codes$ch_type)
channel_codes$ch_identity <- as.factor(channel_codes$ch_identity)

#Importing dem purpose codes. Right now these are the "loose" codings. More narrow options exist in dempurposecodes,csv
dempurposecodes <- read_csv("dempurposecodes2.csv")
dempurposecodes <- dempurposecodes %>%
  filter(dem_purpose==1)%>%
  select(PurposeCode)
```

```{r crs_program}
#This is a function that takes a by year crs_data set, a set of channel codes, and a set of dem purpose codes. It removes unneeded variables and filters out NAs. It then recodes projects with our channel codes which are broader than the original ones. It also gets rid of observations that are not in our set of dem_purpose codes. Finally it reshapes the data a bit to poop out a data frame with observations that are RECIPIENT-YEAR. Variables include the total amount of aid overall and by each channel type. Percentages are also caculated by each channel type.

crs_reshape_ry <- function(crs_data, ch_codes, dempurposecodes){
  
  #This chunk selects necessary variables (donor,recipient, channel, purpose and disbursement) and filters
  #out unwanted donors, recipients and obs with missing channel codes.
  crs_data <- crs_data %>%
    select(Year,RecipientCode,RecipientName,
           usd_disbursement,ChannelCode,PurposeCode,PurposeName) %>%
    filter(!(RecipientCode %in% c(88,189,289,489,689,389,380,298,798,889,789,679,498,9998,589))) %>%
    filter(PurposeCode %in% dempurposecodes$PurposeCode) %>%
    #At present, this function does not remove nonstate donors.
    filter(!is.na(ChannelCode))
  #merge with channelcodes
  crs_data <- merge(crs_data, channel_codes, by.x = 'ChannelCode', by.y = 'code', all.x = TRUE)
  #counts and aid totals for all types
  crs_data <- crs_data %>%
    group_by(Year,RecipientCode) %>%
    add_count(sort = TRUE) %>%
    mutate(total_disbursement = sum(usd_disbursement, na.rm = TRUE)) %>%
    ungroup()
  
  #This giant block splits it up by type and subtype-identity. 
  crs_data2 <- crs_data %>%
    group_by(Year,RecipientCode,ch_type) %>%
    mutate(
      gov_d_total = ifelse(ch_type == 'government'&ch_identity=='donor',sum(usd_disbursement,na.rm = TRUE),0),
      gov_r_total = ifelse(ch_type == 'government'&ch_identity=='recipient',sum(usd_disbursement,na.rm = TRUE),0),
      gov_o_total = ifelse(ch_type == 'government'&ch_identity=='other',sum(usd_disbursement,na.rm = TRUE),0),
      gov_3_total = ifelse(ch_type == 'government'&ch_identity=='thirdparty',sum(usd_disbursement,na.rm = TRUE),0),
      gov_total = ifelse(ch_type == 'government',sum(usd_disbursement, na.rm = TRUE),0),
      corp_total = ifelse(ch_type == 'corporation'|ch_type=='publicprivate',sum(usd_disbursement,na.rm = TRUE),0),
      ngo_total = ifelse(ch_type == 'ngo'|ch_type=='network'|ch_type=='edu',sum(usd_disbursement,na.rm = TRUE),0),
      igo_total = ifelse(ch_type == 'igo',sum(usd_disbursement,na.rm = TRUE),0),
      other_total = ifelse(ch_type == 'government'&ch_identity=='donor',sum(usd_disbursement,na.rm = TRUE),0)
    ) %>%
    ungroup() %>%
    group_by(Year,RecipientCode) %>%
    select(Year,RecipientCode,RecipientName,n,total_disbursement,gov_total,gov_d_total,gov_r_total,
           gov_3_total,gov_o_total,corp_total,ngo_total,igo_total,other_total) %>%
    mutate(
      gov_d_total = max(round(gov_d_total,6), na.rm = TRUE),
      gov_r_total = max(round(gov_r_total,6), na.rm = TRUE),
      gov_3_total = max(round(gov_3_total,6), na.rm = TRUE),
      gov_o_total = max(round(gov_o_total,6), na.rm = TRUE),
      gov_total = max(round(gov_total,6), na.rm = TRUE),
      corp_total = max(round(corp_total,6), na.rm = TRUE),
      ngo_total = max(round(ngo_total,6), na.rm = TRUE),
      igo_total = max(round(igo_total,6), na.rm = TRUE),
      other_total = max(round(other_total,6), na.rm = TRUE)
    ) %>%
    unique() %>%
    ungroup() %>%
    mutate(
      gov_d_percent = round(gov_d_total / total_disbursement,3),
      gov_r_percent = round(gov_r_total / total_disbursement,3),
      gov_o_percent = round(gov_o_total / total_disbursement,3),
      gov_3_percent = round(gov_3_total / total_disbursement,3),
      corp_percent = round(corp_total / total_disbursement,3),
      ngo_percent = round(ngo_total / total_disbursement,3),
      igo_percent = round(igo_total / total_disbursement,3),
      other_percent = round(other_total / total_disbursement,3),
      gov_percent = round(gov_total / total_disbursement,3)
    ) %>%
    #So this idea came from Jill. I'm incluing dummies if the type of aid was the majority type of aid in that country year. The thought is that changes from one percentage point to another might not be that important or noticable to democracy but that a shift in the majority type would cause change. 
    mutate(
      gov_maj = ifelse(gov_percent == max(gov_percent,corp_percent,igo_percent,ngo_percent,other_percent),1,0),
      corp_maj = ifelse(corp_percent == max(gov_percent,corp_percent,igo_percent,ngo_percent,other_percent),1,0),
      igo_maj = ifelse(igo_percent == max(gov_percent,corp_percent,igo_percent,ngo_percent,other_percent),1,0),
      ngo_maj = ifelse(ngo_percent == max(gov_percent,corp_percent,igo_percent,ngo_percent,other_percent),1,0),
      other_maj = ifelse(other_percent == max(gov_percent,corp_percent,igo_percent,ngo_percent,other_percent),1,0)
    )
  #Return the data frame.
  crs_data2
}
```

```{r import_crs_data, message=FALSE}
#This chunk imports and merges all of the yearly CRS data according to the above function.
#vector of the file name years. Early ones are grouped together. 1973-94 is omitted as it serves as the base case below.
years <- c('1995-99','2000-01','2002-03','2004-05','2006','2007','2008','2009','2010','2011','2012','2013','2014','2015','2016')

#importing and running crs_by_types on the base case
load(file = './CRS 1973-94 data.RData')
crs_by_types <- crs_reshape_ry(crs_tmp,channel_codes,dempurposecodes)

#importing, reshaping and appending each of the CRS data files.
for (i in years){
  filepath = paste0('./CRS ',i,' data.RData')
  load(file = filepath)
  tmp_df <- crs_reshape_ry(crs_tmp, channel_codes,dempurposecodes)
  crs_by_types <- rbind(crs_by_types, tmp_df)
}

```

Here are some descriptive statistics on the recipient-year data.
```{r, message = FALSE, results='asis'}
crs_by_types$RecipientName <- ifelse(crs_by_types$RecipientCode==247,"Cote d Ivoire",crs_by_types$RecipientName)

crs_by_types <- crs_by_types %>%
  filter(round(total_disbursement) != 0) %>%
  filter(Year>2003)

tmp <- crs_by_types %>%
  select(Year,RecipientName,total_disbursement,gov_d_percent,gov_r_percent,gov_3_percent,gov_o_percent,corp_percent,igo_percent,ngo_percent,other_percent) %>%
  unique() %>%
  group_by(Year) %>%
  mutate(
          sum_total = sum(total_disbursement, na.rm = TRUE), 
          mean_disbursement = mean(total_disbursement, na.rm = TRUE), 
          mean_gov_d = mean(gov_d_percent, na.rm = TRUE),
          mean_gov_r = mean(gov_r_percent, na.rm = TRUE),
          mean_gov_3 = mean(gov_3_percent, na.rm = TRUE),
          mean_gov_o = mean(gov_o_percent, na.rm = TRUE),
          mean_corp = mean(corp_percent, na.rm = TRUE),
          mean_ngo = mean(ngo_percent, na.rm = TRUE),
          mean_igo = mean(igo_percent, na.rm = TRUE),
          mean_other = mean(other_percent, na.rm = TRUE)
          )  %>%
  select(Year, sum_total, mean_disbursement, mean_gov_d, mean_gov_r, mean_gov_3, mean_gov_o, mean_corp, mean_igo, mean_ngo, mean_other) %>%
  unique()

stargazer(as.data.frame(tmp), digits = 2, type = 'latex', summary = FALSE, title = "Summary Statistics By Year", float.env = 'sidewaystable')

tmp <- crs_by_types %>%
  select(Year,RecipientName,total_disbursement,gov_d_percent,gov_r_percent,gov_3_percent,gov_o_percent,corp_percent,igo_percent,ngo_percent,other_percent) %>%
  unique() %>%
  group_by(RecipientName) %>%
  mutate(
          sum_total = sum(total_disbursement, na.rm = TRUE), 
          mean_disbursement = mean(total_disbursement, na.rm = TRUE), 
          mean_gov_d = mean(gov_d_percent, na.rm = TRUE),
          mean_gov_r = mean(gov_r_percent, na.rm = TRUE),
          mean_gov_3 = mean(gov_3_percent, na.rm = TRUE),
          mean_gov_o = mean(gov_o_percent, na.rm = TRUE),
          mean_corp = mean(corp_percent, na.rm = TRUE),
          mean_ngo = mean(ngo_percent, na.rm = TRUE),
          mean_igo = mean(igo_percent, na.rm = TRUE),
          mean_other = mean(other_percent, na.rm = TRUE)
          )  %>%
  select(RecipientName, sum_total, mean_disbursement, mean_gov_d, mean_gov_r, mean_gov_3, mean_gov_o, mean_corp, mean_igo, mean_ngo, mean_other) %>%
  unique()
stargazer(as.data.frame(tmp),digits = 2, font.size = 'tiny', type = 'latex', summary = FALSE, title = 'Summary Statistics by Recipient')

```


```{r import_and_merge_controls}

crs_by_types$new.code <- countrycode(crs_by_types$RecipientName, origin = 'country.name', destination = 'iso3n')
load("C:/Users/Jack/Google Drive/Active Papers/AidProjects/CRS 2016 data/Freedom House.RData")
x$new.code <- countrycode(x$country, origin = 'country.name', destination = 'iso3n')

working <- merge(crs_by_types, x, by.x = c('Year','new.code'), by.y = c('year','new.code'))
working <- working %>%
  filter(!is.na(Year)&!is.na(new.code))

p4v2017d <- read_excel("p4v2017.xls")
polity <- p4v2017d %>%
  filter(year >2004) %>%
  select(country, year, polity,polity2)

polity$new.code <- countrycode(polity$country, origin = 'country.name', destination = 'iso3n')
working <- merge(working, polity, by.x = c('Year','new.code'), by.y = c('year','new.code'), all.x = TRUE)


#Use this code to import and reformat vdem variables from scratch.
#vdem <- read_csv("Country_Year_V-Dem_Extended_CSV_v8/Country_Year_V-Dem_Extended_CSV_v8/V-Dem-CY+Others-v8.csv")
#vdem <- vdem %>%
#  select(country_name,year,COWcode,v2x_polyarchy,v2x_libdem,v2x_partipdem,v2x_delibdem,v2x_egaldem,
#         e_fh_cl,e_fh_pair,e_fh_pr,e_fh_rol,e_fh_status) %>%
#  filter(year>1993)
#vdem$new.code <- countrycode(vdem$COWcode, origin = 'cown', destination = 'iso3n')

load('./vdem.RData')


working <- merge(working, vdem, by.x = c('Year','new.code'),by.y = c('year','new.code'))

##Pulling in some basic controls from the World Bank
gdp <- wb(country = 'all', indicator = 'NY.GDP.PCAP.CD', startdate = '2003', enddate = '2018') %>%
  rename(gdp = value, year = date) %>%
  select(iso3c, year, gdp)
urban <- wb(country = 'all', indicator = 'SP.URB.TOTL.IN.ZS', startdate = '2003', enddate = '2018') %>%
  rename(urban = value, year = date) %>%
  select(iso3c,year,urban)
pop <- wb(country = 'all', indicator = 'SP.POP.TOTL', startdate = '2003', enddate = '2018') %>%
  rename(pop = value, year = date) %>%
  select(iso3c,year,pop)
controls <- merge(gdp,merge(urban, pop, by = c('iso3c','year')), by = c('iso3c','year'))

controls$new.code <- countrycode(controls$iso3c, origin = 'iso3c', destination = 'iso3n')

controls <- controls %>%
  select(new.code,year,gdp,urban,pop)
working <- merge(working, controls, by.x = c('Year','new.code'), by.y = c('year','new.code'), all.x = TRUE)
```

```{r recipient_year_models, message=FALSE, results='asis', warning=FALSE}
dep.vars <- c('v2x_polyarchy','v2x_libdem','v2x_partipdem','v2x_delibdem','v2x_egaldem','polity2','e_fh_cl',
              'e_fh_pair','e_fh_pr','e_fh_rol','e_fh_status')

ind.vars.base <- c('gov_d_percent','gov_r_percent','gov_3_percent','gov_o_percent', 'ngo_percent', 'igo_percent',
                  'corp_percent', 'log(total_disbursement)')

ind.vars.controlled <- c('gov_d_percent','gov_r_percent','gov_3_percent','gov_o_percent', 'ngo_percent', 'igo_percent',
                  'corp_percent', 'log(total_disbursement)','log(gdp)','urban','log(pop)')

ind.vars.gov_together <- c('I(gov_d_percent+gov_r_percent+gov_3_percent+gov_o_percent)', 'ngo_percent', 'igo_percent',
              'corp_percent', 'log(total_disbursement)', 'log(gdp)','urban','log(pop)')

ind.vars.maj <- c('gov_maj','corp_maj','igo_maj','ngo_maj','log(total_disbursement)')

ind.vars.maj_controlled <- c('gov_maj','corp_maj','igo_maj','ngo_maj','log(total_disbursement)','log(gdp)','urban','log(pop)')

ind.vars.total <- c('log(gov_d_total+1)','log(gov_r_total+1)','log(gov_3_total+1)','log(gov_o_total+1)','log(ngo_total+1)','log(igo_total+1)','log(corp_total+1)')

ind.vars.total.controlled <- c('log(gov_d_total+1)','log(gov_r_total+1)','log(gov_3_total+1)','log(gov_o_total+1)','log(ngo_total+1)','log(igo_total+1)','log(corp_total+1)','log(gdp)','urban','log(pop)')

ind.vars.total.gov_together <- c('log(gov_d_total+gov_r_total+gov_3_total+gov_o_total+1)','log(ngo_total+1)','log(igo_total+1)','log(corp_total+1)','log(gdp)','urban','log(pop)')

for (i in dep.vars){
  mod.base <- plm(as.formula(paste(i, paste(c(ind.vars.total,paste0('lag(',i,')')),collapse = '+'),sep = '~')), model = 'within',data = working,index = c('RecipientCode'))
  mod.controlled <- plm(as.formula(paste(i, paste(c(ind.vars.total.controlled,paste0('lag(',i,')')),collapse = '+'),sep = '~')), model = 'within',data = working,index = c('RecipientCode'))
  mod.gov_together <- plm(as.formula(paste(i, paste(c(ind.vars.total.gov_together,paste0('lag(',i,')')),collapse = '+'),sep = '~')), model = 'within',data = working,index = c('RecipientCode'))
  mod.base.re <- plm(as.formula(paste(i, paste(c(ind.vars.total,paste0('lag(',i,')')),collapse = '+'),sep = '~')), model = 'random',data = working,index = c('RecipientCode'))
  mod.controlled.re <- plm(as.formula(paste(i, paste(c(ind.vars.total.controlled,paste0('lag(',i,')')),collapse = '+'),sep = '~')), model = 'random',data = working,index = c('RecipientCode'))
  #mod.maj <- plm(as.formula(paste(i, paste(ind.vars.maj,collapse = '+'),sep = '~')), model = 'within',data = working,index = c('RecipientCode'))
  #mod.maj_controlled <- plm(as.formula(paste(i, paste(ind.vars.maj_controlled,collapse = '+'),sep = '~')), model = 'within',data = working,index = c('RecipientCode'))
  titlevar <- paste0('Recipient-Year: ',ifelse(i == 'v2x_polyarchy','VDEM Polyarchy', ifelse(i == 'v2x_libdem','VDEM LibDem',ifelse(i == 'v2x_delibdem','VDEM DelibDem',ifelse(i == 'v2x_egaldem','VDEM EgalDem',ifelse(i == 'v2x_partipdem','VDEM PartipDem',ifelse(i == 'polity2','Polity',ifelse(i == 'e_fh_cl','FH Civil Liberties',ifelse(i == 'e_fh_pr','FH Proportional Rep',ifelse(i == 'e_fh_status','FH Status',ifelse(i == 'e_fh_rol','FH Rule of Law','FH Personal Autonomy')))))))))))
  
  stargazer(mod.base,mod.controlled,mod.gov_together,mod.base.re, mod.controlled.re, colnames = FALSE, font.size = 'small', dep.var.labels = c('Base','Controls','Gov Together','Base RE','Controls RE'), title = titlevar, column.sep.width = "1pt", float.env = "sidewaystable", covariate.labels = c('Donor Gov','Recip Gov','Third Gov','Other Gov','All Gov','NGO','IGO','Corporation','log(GDP)','Urban','log(Population)','Lagged DV'), model.numbers = FALSE)
  }

```


##Analysis by Dyad-Year
```{r dyad_crs_program}
#This is a function that takes a by year crs_data set, a set of channel codes, and a set of dem purpose codes. It removes unneeded variables and filters out NAs. It then recodes projects with our channel codes which are broader than the original ones. It also gets rid of observations that are not in our set of dem_purpose codes. Finally it reshapes the data a bit to poop out a data frame with observations that are RECIPIENT-YEAR. Variables include the total amount of aid overall and by each channel type. Percentages are also caculated by each channel type.

crs_reshape_dy <- function(crs_data, ch_codes, dempurposecodes){
  
  #This chunk selects necessary variables (donor,recipient, channel, purpose and disbursement) and filters
  #out unwanted donors, recipients and obs with missing channel codes.
  crs_data <- crs_data %>%
    select(Year,RecipientCode,RecipientName,DonorCode,DonorName,
           usd_disbursement,ChannelCode,PurposeCode,PurposeName) %>%
    filter(!(RecipientCode %in% c(88,189,289,489,689,389,380,298,798,889,789,679,498,9998,589))) %>%
    filter(PurposeCode %in% dempurposecodes$PurposeCode) %>%
    filter(DonorCode %in% c(1,2,3,4,5,6,7,8,9,10,11,12,13,18,20,21,22,40,50,61,68,69,75,76,301,302,701,742,801,820,
                            30,45,55,62.70,72,77,82,83,84,87,130,133,358,543,546,552,561,566,576,611,613,732,764,765)) %>%
    filter(!is.na(ChannelCode))
  #merge with channelcodes
  crs_data <- merge(crs_data, channel_codes, by.x = 'ChannelCode', by.y = 'code', all.x = TRUE)
  #counts and aid totals for all types
  crs_data <- crs_data %>%
    group_by(Year,DonorCode,RecipientCode) %>%
    add_count(sort = TRUE) %>%
    mutate(total_disbursement = sum(usd_disbursement, na.rm = TRUE)) %>%
    ungroup()
  
  #This giant block splits it up by type and subtype-identity. 
  crs_data2 <- crs_data %>%
    group_by(Year,RecipientCode,DonorCode,ch_type) %>%
    mutate(
      gov_d_total = ifelse(ch_type == 'government'&ch_identity=='donor',sum(usd_disbursement,na.rm = TRUE),0),
      gov_r_total = ifelse(ch_type == 'government'&ch_identity=='recipient',sum(usd_disbursement,na.rm = TRUE),0),
      gov_o_total = ifelse(ch_type == 'government'&ch_identity=='other',sum(usd_disbursement,na.rm = TRUE),0),
      gov_3_total = ifelse(ch_type == 'government'&ch_identity=='thirdparty',sum(usd_disbursement,na.rm = TRUE),0),
      gov_total = ifelse(ch_type == 'government',sum(usd_disbursement, na.rm = TRUE),0),
      corp_total = ifelse(ch_type == 'corporation'|ch_type=='publicprivate',sum(usd_disbursement,na.rm = TRUE),0),
      ngo_total = ifelse(ch_type == 'ngo'|ch_type=='network'|ch_type=='edu',sum(usd_disbursement,na.rm = TRUE),0),
      igo_total = ifelse(ch_type == 'igo',sum(usd_disbursement,na.rm = TRUE),0),
      other_total = ifelse(ch_type == 'government'&ch_identity=='donor',sum(usd_disbursement,na.rm = TRUE),0)
    ) %>%
    ungroup() %>%
    group_by(Year,DonorCode,RecipientCode) %>%
    select(Year,RecipientCode,RecipientName,DonorCode,DonorName,n,total_disbursement,gov_total,gov_d_total,gov_r_total, gov_3_total,gov_o_total,corp_total,ngo_total,igo_total,other_total) %>%
    mutate(
      gov_d_total = max(round(gov_d_total,6), na.rm = TRUE),
      gov_r_total = max(round(gov_r_total,6), na.rm = TRUE),
      gov_3_total = max(round(gov_3_total,6), na.rm = TRUE),
      gov_o_total = max(round(gov_o_total,6), na.rm = TRUE),
      gov_total = max(round(gov_total,6), na.rm = TRUE),
      corp_total = max(round(corp_total,6), na.rm = TRUE),
      ngo_total = max(round(ngo_total,6), na.rm = TRUE),
      igo_total = max(round(igo_total,6), na.rm = TRUE),
      other_total = max(round(other_total,6), na.rm = TRUE)
    ) %>%
    unique() %>%
    ungroup() %>%
    mutate(
      gov_d_percent = round(gov_d_total / total_disbursement,3),
      gov_r_percent = round(gov_r_total / total_disbursement,3),
      gov_o_percent = round(gov_o_total / total_disbursement,3),
      gov_3_percent = round(gov_3_total / total_disbursement,3),
      corp_percent = round(corp_total / total_disbursement,3),
      ngo_percent = round(ngo_total / total_disbursement,3),
      igo_percent = round(igo_total / total_disbursement,3),
      other_percent = round(other_total / total_disbursement,3),
      gov_percent = round(gov_total / total_disbursement,3)
    ) %>%
    #So this idea came from Jill. I'm incluing dummies if the type of aid was the majority type of aid in that country year. The thought is that changes from one percentage point to another might not be that important or noticable to democracy but that a shift in the majority type would cause change. 
    mutate(
      gov_maj = ifelse(gov_percent == max(gov_percent,corp_percent,igo_percent,ngo_percent,other_percent),1,0),
      corp_maj = ifelse(corp_percent == max(gov_percent,corp_percent,igo_percent,ngo_percent,other_percent),1,0),
      igo_maj = ifelse(igo_percent == max(gov_percent,corp_percent,igo_percent,ngo_percent,other_percent),1,0),
      ngo_maj = ifelse(ngo_percent == max(gov_percent,corp_percent,igo_percent,ngo_percent,other_percent),1,0),
      other_maj = ifelse(other_percent == max(gov_percent,corp_percent,igo_percent,ngo_percent,other_percent),1,0)
    )
  #Return the data frame.
  crs_data2
}
```

```{r dyad_import_crs_data, message=FALSE}
#This chunk imports and merges all of the yearly CRS data according to the above function.
#vector of the file name years. Early ones are grouped together. 1973-94 is omitted as it serves as the base case below.
years <- c('1995-99','2000-01','2002-03','2004-05','2006','2007','2008','2009','2010','2011','2012','2013','2014','2015','2016')

#importing and running crs_by_types on the base case
load(file = './CRS 1973-94 data.RData')
crs_by_types <- crs_reshape_dy(crs_tmp,channel_codes,dempurposecodes)

#importing, reshaping and appending each of the CRS data files.
for (i in years){
  filepath = paste0('./CRS ',i,' data.RData')
  load(file = filepath)
  tmp_df <- crs_reshape_dy(crs_tmp, channel_codes,dempurposecodes)
  crs_by_types <- rbind(crs_by_types, tmp_df)
}

```

Here are some descriptive statistics on the recipient-year data.
```{, message = FALSE, results='asis'}
crs_by_types$RecipientName <- ifelse(crs_by_types$RecipientCode==247,"Cote d Ivoire",crs_by_types$RecipientName)

crs_by_types <- crs_by_types %>%
  filter(round(total_disbursement) != 0) %>%
  filter(Year>2003)

tmp <- crs_by_types %>%
  select(Year,RecipientName,DonorName,total_disbursement,gov_d_percent,gov_r_percent,gov_3_percent,gov_o_percent,corp_percent,igo_percent,ngo_percent,other_percent) %>%
  unique() %>%
  group_by(Year) %>%
  mutate(
          sum_total = sum(total_disbursement, na.rm = TRUE), 
          mean_disbursement = mean(total_disbursement, na.rm = TRUE), 
          mean_gov_d = mean(gov_d_percent, na.rm = TRUE),
          mean_gov_r = mean(gov_r_percent, na.rm = TRUE),
          mean_gov_3 = mean(gov_3_percent, na.rm = TRUE),
          mean_gov_o = mean(gov_o_percent, na.rm = TRUE),
          mean_corp = mean(corp_percent, na.rm = TRUE),
          mean_ngo = mean(ngo_percent, na.rm = TRUE),
          mean_igo = mean(igo_percent, na.rm = TRUE),
          mean_other = mean(other_percent, na.rm = TRUE)
          )  %>%
  select(Year, sum_total, mean_disbursement, mean_gov_d, mean_gov_r, mean_gov_3, mean_gov_o, mean_corp, mean_igo, mean_ngo, mean_other) %>%
  unique()

stargazer(as.data.frame(tmp), digits = 2, type = 'latex', summary = FALSE, title = "Dyadic Summary Statistics By Year")

tmp <- crs_by_types %>%
  select(Year,RecipientName,DonorName,total_disbursement,gov_d_percent,gov_r_percent,gov_3_percent,gov_o_percent,corp_percent,igo_percent,ngo_percent,other_percent) %>%
  unique() %>%
  group_by(RecipientName,DonorName) %>%
  mutate(
          sum_total = sum(total_disbursement, na.rm = TRUE), 
          mean_disbursement = mean(total_disbursement, na.rm = TRUE), 
          mean_gov_d = mean(gov_d_percent, na.rm = TRUE),
          mean_gov_r = mean(gov_r_percent, na.rm = TRUE),
          mean_gov_3 = mean(gov_3_percent, na.rm = TRUE),
          mean_gov_o = mean(gov_o_percent, na.rm = TRUE),
          mean_corp = mean(corp_percent, na.rm = TRUE),
          mean_ngo = mean(ngo_percent, na.rm = TRUE),
          mean_igo = mean(igo_percent, na.rm = TRUE),
          mean_other = mean(other_percent, na.rm = TRUE)
          )  %>%
  select(RecipientName,DonorName, sum_total, mean_disbursement, mean_gov_d, mean_gov_r, mean_gov_3, mean_gov_o, mean_corp, mean_igo, mean_ngo, mean_other) %>%
  unique()
stargazer(as.data.frame(tmp),digits = 2, font.size = 'small', type = 'latex', summary = FALSE, title = 'Summary Statistics by Dyad')

```


```{r dyad_import_and_merge_controls}

crs_by_types$new.code <- countrycode(crs_by_types$RecipientName, origin = 'country.name', destination = 'iso3n')
load(file = "./Freedom House.RData")
x$new.code <- countrycode(x$country, origin = 'country.name', destination = 'iso3n')

working <- merge(crs_by_types, x, by.x = c('Year','new.code'), by.y = c('year','new.code'))
working <- working %>%
  filter(!is.na(Year)&!is.na(new.code))

p4v2017d <- read_excel("p4v2017.xls")
polity <- p4v2017d %>%
  filter(year >2004) %>%
  select(country, year, polity,polity2)

polity$new.code <- countrycode(polity$country, origin = 'country.name', destination = 'iso3n')
working <- merge(working, polity, by.x = c('Year','new.code'), by.y = c('year','new.code'), all.x = TRUE)


#Use this code to import and reformat vdem variables from scratch.
#vdem <- read_csv("Country_Year_V-Dem_Extended_CSV_v8/Country_Year_V-Dem_Extended_CSV_v8/V-Dem-CY+Others-v8.csv")
#vdem <- vdem %>%
#  select(country_name,year,COWcode,v2x_polyarchy,v2x_libdem,v2x_partipdem,v2x_delibdem,v2x_egaldem,
#         e_fh_cl,e_fh_pair,e_fh_pr,e_fh_rol,e_fh_status) %>%
#  filter(year>1993)
#vdem$new.code <- countrycode(vdem$COWcode, origin = 'cown', destination = 'iso3n')

load('./vdem.RData')


working <- merge(working, vdem, by.x = c('Year','new.code'),by.y = c('year','new.code'))

working$DyadName <- paste(working$DonorName,working$RecipientName,sep = '-')

##Pulling in some basic controls from the World Bank
gdp <- wb(country = 'all', indicator = 'NY.GDP.PCAP.CD', startdate = '2003', enddate = '2018') %>%
  rename(gdp = value, year = date) %>%
  select(iso3c, year, gdp)
urban <- wb(country = 'all', indicator = 'SP.URB.TOTL.IN.ZS', startdate = '2003', enddate = '2018') %>%
  rename(urban = value, year = date) %>%
  select(iso3c,year,urban)
pop <- wb(country = 'all', indicator = 'SP.POP.TOTL', startdate = '2003', enddate = '2018') %>%
  rename(pop = value, year = date) %>%
  select(iso3c,year,pop)
controls <- merge(gdp,merge(urban, pop, by = c('iso3c','year')), by = c('iso3c','year'))

controls$new.code <- countrycode(controls$iso3c, origin = 'iso3c', destination = 'iso3n')

controls <- controls %>%
  select(new.code,year,gdp,urban,pop)
working <- merge(working, controls, by.x = c('Year','new.code'), by.y = c('year','new.code'), all.x = TRUE)

working <- working %>%
  filter(!is.na(DyadName))
```

```{r dyad_year_models, message=FALSE, results='asis', warning=FALSE}
dep.vars <- c('v2x_polyarchy','v2x_libdem','v2x_partipdem','v2x_delibdem','v2x_egaldem','polity2','e_fh_cl',
              'e_fh_pair','e_fh_pr','e_fh_rol','e_fh_status')

ind.vars.base <- c('gov_d_percent','gov_r_percent','gov_3_percent','gov_o_percent', 'ngo_percent', 'igo_percent',
                  'corp_percent', 'log(total_disbursement)')

ind.vars.controlled <- c('gov_d_percent','gov_r_percent','gov_3_percent','gov_o_percent', 'ngo_percent', 'igo_percent',
                  'corp_percent', 'log(total_disbursement)','log(gdp)','urban','log(pop)')

ind.vars.gov_together <- c('I(gov_d_percent+gov_r_percent+gov_3_percent+gov_o_percent)', 'ngo_percent', 'igo_percent',
              'corp_percent', 'log(total_disbursement)', 'log(gdp)','urban','log(pop)')

ind.vars.maj <- c('gov_maj','corp_maj','igo_maj','ngo_maj','log(total_disbursement)')

ind.vars.maj_controlled <- c('gov_maj','corp_maj','igo_maj','ngo_maj','log(total_disbursement)','log(gdp)','urban','log(pop)')

ind.vars.total <- c('log(gov_d_total+1)','log(gov_r_total+1)','log(gov_3_total+1)','log(gov_o_total+1)','log(ngo_total+1)','log(igo_total+1)','log(corp_total+1)')

ind.vars.total.controlled <- c('log(gov_d_total+1)','log(gov_r_total+1)','log(gov_3_total+1)','log(gov_o_total+1)','log(ngo_total+1)','log(igo_total+1)','log(corp_total+1)','log(gdp)','urban','log(pop)')

ind.vars.total.gov_together <- c('log(gov_d_total+gov_r_total+gov_3_total+gov_o_total+1)','log(ngo_total+1)','log(igo_total+1)','log(corp_total+1)','log(gdp)','urban','log(pop)')

for (i in dep.vars){
  mod.base <- plm(as.formula(paste(i, paste(c(ind.vars.total,paste0('lag(',i,')')),collapse = '+'),sep = '~')), model = 'within',data = working,index = c('RecipientCode'))
  mod.controlled <- plm(as.formula(paste(i, paste(c(ind.vars.total.controlled,paste0('lag(',i,')')),collapse = '+'),sep = '~')), model = 'within',data = working,index = c('RecipientCode'))
  mod.gov_together <- plm(as.formula(paste(i, paste(c(ind.vars.total.gov_together,paste0('lag(',i,')')),collapse = '+'),sep = '~')), model = 'within',data = working,index = c('RecipientCode'))
  mod.base.re <- plm(as.formula(paste(i, paste(c(ind.vars.total,paste0('lag(',i,')')),collapse = '+'),sep = '~')), model = 'random',data = working,index = c('RecipientCode'))
  mod.controlled.re <- plm(as.formula(paste(i, paste(c(ind.vars.total.controlled,paste0('lag(',i,')')),collapse = '+'),sep = '~')), model = 'random',data = working,index = c('RecipientCode'))
  #mod.maj <- plm(as.formula(paste(i, paste(ind.vars.maj,collapse = '+'),sep = '~')), model = 'within',data = working,index = c('RecipientCode','DonorCode'))
  #mod.maj_controlled <- plm(as.formula(paste(i, paste(ind.vars.maj_controlled,collapse = '+'),sep = '~')), model = 'within',data = working,index = c('RecipientCode','DonorCode'))
  titlevar <- paste0('Dyadic Year: ',ifelse(i == 'v2x_polyarchy','VDEM Polyarchy', ifelse(i == 'v2x_libdem','VDEM LibDem',ifelse(i == 'v2x_delibdem','VDEM DelibDem',ifelse(i == 'v2x_egaldem','VDEM EgalDem',ifelse(i == 'v2x_partipdem','VDEM PartipDem',ifelse(i == 'polity2','Polity',ifelse(i == 'e_fh_cl','FH Civil Liberties',ifelse(i == 'e_fh_pr','FH Proportional Rep',ifelse(i == 'e_fh_status','FH Status',ifelse(i == 'e_fh_rol','FH Rule of Law','FH Personal Autonomy')))))))))))
  
  stargazer(mod.base,mod.controlled,mod.gov_together,mod.base.re, mod.controlled.re, colnames = FALSE, font.size = 'small', dep.var.labels = c('Base','Controls','Gov Together','Base RE','Controls RE'), title = titlevar, column.sep.width = "1pt", float.env = "sidewaystable", covariate.labels = c('Donor Gov','Recip Gov','Third Gov','Other Gov','All Gov','NGO','IGO','Corporation','log(GDP)','Urban','log(Population)','Lagged DV'), model.numbers = FALSE)
  }

```



##Subnational Stuff
